Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-09-30 WSSSPE3/report/wg_appendix_software_credit.tex
Create wg_appendix_software_credit.tex
Update wg_appendix_software_credit.tex
Completed group list

\section{Software Credit Working Group Discussion}

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   Alice Allen           &  Astrophysics Source Code Library (ASCL)
\\ Daniel S. Katz        &  University of Chicago \& Argonne National Laboratory
\end{longtable}
}

\subsection{Summary of Discussion}

\subsection{Description of Opportunity, Challenges, and Obstacles}

\subsection{Key Next Steps}

\subsection{Plan for Future Organization}

\subsection{What Else is Needed?}

\subsection{Key Milestones and Responsible Parties}

\subsection{Description of Funding Needed}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software Credit Working Group Discussion}
\label{sec:appendix_SW_credit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   Alice Allen            &  Astrophysics Source Code Library (ASCL)
\\ Sou-Cheng Choi         &  NORC at the University of Chicago and Illinois Institute of Technology
\\ James Hetherington     &  University College London
\\ Lorraine Hwang         &  University of California, Davis
\\ Daniel S.\ Katz        &  University of Chicago \& Argonne National Laboratory
\\ Frank Löffler          &  Louisiana State University
\\ Abby Cabunoc Mayes     &  Mozilla Science Lab
\\ Kyle E.\ Niemeyer      &  Oregon State University
\\ Grace Peng             &  National Center for Atmospheric Research
\\ Ilian Todorov          &  Science \& Technology Facilities Council, UK
\end{longtable}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Summary of Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description of Opportunity, Challenges, and Obstacles}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Key Next Steps}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Plan for Future Organization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{What Else is Needed?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Key Milestones and Responsible Parties}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description of Funding Needed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
